Databrary: Enabling sharing and reuse of research video

### 2015-04-15 jcdl-15/paper_demo.tex
some changes

Focusing on a particular research domain allows us to develop a tool that is informed by how the intended community of users currently works, while enhancing that labor as well as accomodating the the privacy concerns for data that often has a high disclosure risk.
This has resulted in the creation of a set of data management features that empower researchers to actively manage their own projects---to upload data with accompanying metadata---as each study unfolds. 
To this end, we have designed and implemented a spreadsheet interface for entering, editing, and viewing session-level metadata (e.g., participants, conditions of study, tasks in the experiment, session access levels, study groups and conditions, etc.). 
Most researchers use desktop spreadsheets for precisely this purpose in their own labs, making the interface and functionality intuitive to users. 
We have also implemented a timeline for uploading, viewing, and tagging video assets related to sessions.
The timeline view is designed to look and operate like video editing software commonly used in many research labs.
It allows users to upload video files, position them to reflect the temporal order of each component of data collection, and annotate video sections with user-generated tags. 
These tags become additional metadata indices for search and discovery.

@@

\section{Discovery and Scholarly Communication}

@@

As we continue to gather feedback from our intended user base, we not only see Databrary as a tool that facilitates the standardized management of research data, but also as an opportunity to enhance the ability for academics communicate about their research in all of its richness. We already addressed the basic upload, data management, and storage needs of our target community, and have sufficiently answered the question of how to protect sensitive video data while providing wider opportunities to share that data. Going forward, we hope to focus more on developing the tools for searching, discovering, and reusing that data, allowing researchers to work with their data in ways they had not previously imagined.

>>>>

Focusing on a particular research domain allows us to develop a tool that is informed by how the intended community of users currently works, while enhancing that labor as well as accomodating the specific privacy concerns for data that often has a high disclosure risk.
This has resulted in the creation of a set of data management features that empower researchers to actively manage their own projects---to upload data with accompanying metadata---as each study unfolds. 
To this end, we have designed and implemented a spreadsheet interface for entering, editing, and viewing session-level metadata (e.g., participants, conditions of study, tasks in the experiment, session access levels, study groups and conditions, etc.). 
Most researchers use desktop spreadsheets for precisely this purpose in their own labs, making the interface and functionality intuitive to users. 
We have also implemented a timeline for uploading, viewing, and tagging video assets related to sessions.
The timeline view is designed to look and operate like video editing software commonly used in many research labs.
It allows users to upload video files, position them to reflect the temporal order of each component of data collection, and annotate video sections with user-generated tags. 
These tags become additional metadata indices for search and discovery.

@@

\section{Discovery, Reuse, and Next Steps}

@@

As we continue to gather feedback from our intended user base, we not only see Databrary as a tool that facilitates the standardized management of research data, but also as an opportunity to enhance the ability for academics communicate about and augment their research. We already addressed the basic upload, data management, and storage needs of our target community, and have sufficiently answered the question of how to protect sensitive video data while providing wider opportunities to share that data. Going forward, we hope to focus more on developing the tools for searching, discovering, and reusing that data, allowing researchers to work with their data in ways they had not previously imagined.
